A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Fix links and trim
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1079 43ef1190-90fd-4dd7-a769-d0121f02b80e

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients may use these values to retrieve
the updated response only if the resource has changed. Other relevant
headers are described in % a companion technical report
%\cite{kjernsmo_add_survey_2015}.
 Table~\ref{tab:headers}.
\todo{More on HTTP}

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN), as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in the companion technical report
\cite{kjernsmo_add_survey_2015}.% Appendix~\ref{app:reduction}.

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider detailed in the companion technical report
\cite{kjernsmo_add_survey_2015}, resulting in 7745 requests, done on
2015-01-02.

@@

Key challenges to the validity of the survey are biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples in the crawl is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represent the breadth of the Semantic Web, momentarily at least.

@@

The analysis is focused on finding descriptive statistics to
understand how different servers support caching, for how long
resources hosted with those that do support caching may be considered
fresh, if it is possible to easily compute a heuristic freshness
lifetime, and revalidate the response on expiry. Apart from quoting
the numbers we aggregated, we do this by presenting summarized data
distribution visualizations, to allow for an intuitive understanding
of the data. Where appropriate, we also do statistical hypothesis
tests.

@@

The companion technical report \cite{kjernsmo_add_survey_2015} lists other caching
headers than those mentioned in the introduction. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

>>>>

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients may use these values to retrieve
the updated response only if the resource has changed. Other relevant
headers are described in Table~\ref{tab:headers}.
\todo{More on HTTP}

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN), as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in a companion technical report
\cite{kjernsmo_add_survey_2015}.

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider also detailed in
\cite{kjernsmo_add_survey_2015}, resulting in 7745 requests, done on
2015-01-02.

@@

Key challenges to the validity of the survey are biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represent the breadth of the Semantic Web, momentarily at least.

@@

The analysis is focused on finding descriptive statistics to
understand how different servers support caching, for how long
resources hosted with those that do support caching may be considered
fresh, if it is possible to easily compute a heuristic freshness
lifetime, and revalidate the response on expiry. Apart from quoting
the numbers we aggregated, we do this by presenting summarized data
distribution visualizations, to allow for an intuitive understanding
of the data. Where appropriate, we also do statistical hypothesis
tests, using so-called contingency tables, see
\cite{kjernsmo_add_survey_2015} for details.

@@

We also looked for other headers in \ref{tab:headers}. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.
